Stage-Splitting a Modal Language

### 2014-06-20 paper/paper.tex
adding listings stuff

\lstset{language=ML,
        columns=fullflexible,
        basicstyle=\ttfamily,
        tabsize=4,
        escapeinside={"*}{*"},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {$}{{$\fut$}}1}

>>>>

\lstset{language=ML,
        columns=fullflexible,
        basicstyle=\ttfamily,
        tabsize=4,
        escapeinside={"*}{*"},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {$}{{$\fut$}}1}
